Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2023-01-09 sports_analytics.Rmd
small updates on bayesian state-space

@macdonald2012expected uses expected goals to evaluate ice hockey players, but does not have access to player tracking data necessary to evaluate possessions.
@kumagai2021hockey offer an EPV metric for ice hockey.

@@

@koopman2015dynamic use a Bayesian state-space model to develop team ratings for English Premier League soccer that improves on bookmaker's odds.

>>>>

@macdonald2012expected uses expected goals to evaluate ice hockey players, but does not have access to player tracking data necessary to evaluate possessions.
@kumagai2021hockey offer an EPV metric for ice hockey via a Bayesian space-time framework.

@@

In a similar Bayesian setting, @koopman2015dynamic studies English Premier League soccer match results by assuming a bivariate Poisson distribution with time-varying team abilities.
This state-space approach appears to improve on bookmaker's odds.
